---
title: "Machine Learing Prediction Project"
author: "Abul Kayash"
date: "14 August 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Background
Using devices such as Jawbone Up, Nike FuelBand, and Fitbit it is now possible to collect a large amount of data about personal activity relatively inexpensively. These type of devices are part of the quantified self movement - a group of enthusiasts who take measurements about themselves regularly to improve their health, to find patterns in their behavior. 

The goal of your project is to predict the manner in which they did the exercise.

## Load The Libraries
```{r Load Libraries}
library(knitr)
library(caret)
library(rpart)
library(randomForest)
library(ggplot2)
library(rattle)

```

## Load & CLean Data
```{r Load Data}

trainData <- read.csv("pml-training.csv",na.strings=c("NA","#DIV/0!",""), header=TRUE)
benchMark <- read.csv("pml-testing.csv", na.strings=c("NA","#DIV/0!",""), header=TRUE)

# remove id column as they are unique for each row thus not a useful predictor
trainData <- trainData [,-1] 
benchMark <- benchMark [,-1]


# remove null columns
trainData <- trainData[, unlist(lapply(trainData, function(x) !any(is.na(x))))]
benchMark <- benchMark[, unlist(lapply(benchMark, function(x) !any(is.na(x))))]

dim (trainData)
dim (benchMark)



```



## Prepare Training & Partion Set
```{r Training&Partion}
# Set seed to make results reproducible
set.seed(5315)

inTrain <- createDataPartition(y=trainData$classe , p=0.7, list=FALSE)
training <- trainData[inTrain,]
testing <- trainData[-inTrain,]

dim(testing)
dim(training)

```

## Build Prediction Model
```{r Prediction}

#Build 
controlDTree <- trainControl(method="cv", 5)
modelDTree <- train(classe ~ ., data=training, method="rf", trControl=controlDTree, ntree=150)

#Test the model.
confusionMatrix(predict(modelDTree, testing), testing$classe)

#Very high accuracy rate 99.88%, thus we have a very good model to predict the outcome of the training set.    

predict(modelDTree, benchMark)

```



